Experience Report: Distributed Computing for the Common Man

### 2010-03-24 doc/icfp-2010/main.tex
*** empty log message ***

\begin{abstract}

\end{abstract}

@@

% what it is and what it is not
% \begin{itemize}
% \item it is not a library which does parallelization
% \item it is a library for reliable distributed execution of
%   parallelizable computation 
% \end{itemize}

% inspired by Google's MapReduce~\cite{mapreduce} (itself inspired by functional
% programming, ironically) ;  however, there are differences:
% \begin{itemize}
% \item polymorphic, higher-order API
% \item more generic (cores/network)
% \item does not focus on association lists
% \item we don't have data locality (future work)
% \end{itemize}

% what is the target audience/applications: 
% for instance, use if automatic provers on thousands of verification
% conditions, on computing infrastructures which can be
% \begin{itemize}
% \item a single machine with multiple cores, possibly remote
% \item several machines, small or large in number, over a network
% \end{itemize}

@@

The paper is organized as follows. In Section~\ref{sec:API}, we
describe the main idea behind the generic API, and introduce
\of{master} and \of{worker} programs. In Section~\ref{sec:derived}, we
derive more interesting functions from the generic
API. Section~\ref{sec:implem} delves into the implementation details
of our library, while Section~\ref{sec:experiments} illustrates the
potential of the presented library through experimental evaluation. We
compare our approach with relevant related work in
Section~\ref{sec:future} and outline our future work.

@@

These five functions are the most natural derivations of the
\of{compute} functions. There are obviously other possible derivations
(e.g. a variant of \of{map_fold} where only \of{fold} is meaningful);
in most cases, they could be derived in a straightforward way from our
generic API.

>>>>

\begin{abstract}
  In this paper, we present a distributed computing library for
  functional programming languages. The main features of this library
  include (1) a highly-generic API, (2) several implementations to
  adapt to different computing environments such as sequential,
  multi-core or network, and (3) a reliable fault tolerance mechanism.
  This paper describes the motivation behind this work, as well as
  the design and implementation of the library. It also demonstrates
  the potential of the library with realistic experiments.
\end{abstract}

@@

% what it is and what it is not
% \begin{itemize}
% \item it is not a library which does parallelization
% \item it is a library for reliable distributed execution of
%   parallelizable computation 
% \end{itemize}
% inspired by Google's MapReduce~\cite{mapreduce} (itself inspired by functional
% programming, ironically) ;  however, there are differences:
% \begin{itemize}
% \item polymorphic, higher-order API
% \item more generic (cores/network)
% \item does not focus on association lists
% \item we don't have data locality (future work)
% \end{itemize}
% what is the target audience/applications: 
% for instance, use if automatic provers on thousands of verification
% conditions, on computing infrastructures which can be
% \begin{itemize}
% \item a single machine with multiple cores, possibly remote
% \item several machines, small or large in number, over a network
% \end{itemize}

@@

\medskip
The paper is organized as follows. In Section~\ref{sec:API}, we
describe the main idea behind the generic API, and introduce
\of{master} and \of{worker} programs. In Section~\ref{sec:derived}, we
derive some interesting functions from the generic
API. Section~\ref{sec:implem} delves into the implementation details
of our library, while Section~\ref{sec:experiments} illustrates the
potential of the presented library through experimental evaluation. We
compare our approach with relevant related work in
Section~\ref{sec:future} and outline our future work.

@@

\medskip
These five functions are the most natural derivations of the
\of{compute} functions. There are obviously other possible derivations
(e.g. a variant of \of{map_fold} where only \of{fold} is meaningful);
in most cases, they could be derived in a straightforward way from our
generic API.
